\chapter{Electronic Design}

\graphicspath{{./Figures/Modeling}}



\begin{itemize}
	\item Outline the purpose and scope of the chapter.
	\item Briefly describe the mechanical design's role in the overall project.
\end{itemize}


\section{Design Objectives and Requirements}
\begin{itemize}
	\item Detail the primary objectives of the mechanical design
	\item List the requirements that the design must meet (e.g., weight limits, size constraints, mobility requirements).
\end{itemize}
\section{Assembly Process}
\begin{itemize}
	\item Step-by-step explanation of the assembly process.
	\item Tools and techniques used in the assembly.
	\item Assembly sequence and rationale behind it.
\end{itemize}
\section{Integration of Mechanical and Electronic Systems}
\begin{itemize}
	\item Discussion on how mechanical components interface with electronic systems.
	\item Challenges faced in integration and strategies employed to overcome them.
\end{itemize}
\section{Troubleshooting and Problem Solving}
\begin{itemize}
	\item Discussion of any unexpected challenges or issues faced during assembly.
	\item How these issues were diagnosed and resolved.
\end{itemize}
\section{Safety Considerations}
\begin{itemize}
	\item Safety measures taken during the assembly process.
	\item Design considerations for ensuring the operational safety of the robot.
\end{itemize}
\begin{itemize}
	\item \textbf{Discrete Numerical Simulation:} Elaboration on the process of discrete numerical simulation, including the discrete double integration method to arrive at the state vector.
\end{itemize}
