\chapter{Firmware and Testing}

\graphicspath{{./Figures/Modeling}}

\begin{itemize}
	\item Overview of the chapter's content and its significance in the context of the overall project.
	\item Briefly state the objectives of firmware development and testing procedures.
\end{itemize}


\section{Firmware Development}
\begin{itemize}
	\item Discuss the development environment and tools used for firmware programming.
	\item Detail the architecture and design of the firmware, including flowcharts or state  diagrams if applicable.
	\item Explain the implementation of key functionalities such as control algorithms, sensor integration, and actuator management.
\end{itemize}
\section{Programming Languages and Tools}
\begin{itemize}
	\item List and describe the programming languages used for firmware development.
	\item Mention any specific software tools, libraries, or frameworks employed.
\end{itemize}
\section{Integration with Hardware}
\begin{itemize}
	\item Discuss how the firmware interacts with and controls the hardware components.
	\item Explain any challenges encountered in integration and how they were resolved.
\end{itemize}
\section{Testing Framework and Methodology}
\begin{itemize}
	\item Outline the testing framework used to validate the firmware.
	\item Describe the methodology for functional testing, including unit tests, integration tests, and system-level tests.
\end{itemize}
\section{Test Cases and Scenarios}
\begin{itemize}
	\item Present the results of the testing procedures.
	\item Analyze these results, highlighting successful areas and identifying any issues or bugs discovered.
\end{itemize}
\section{Debugging and Troubleshooting}
\begin{itemize}
	\item Discuss the process of debugging and troubleshooting encountered problems.
	\item Explain how issues were diagnosed and resolved.
\end{itemize}

\begin{notebox}
	the bolts used the problem to shorten them so that it wouldn't touch the motor 
\end{notebox}

